---
title: "RWorksheet#5_group(number)"
author: "Zydrick Ceniza, Aira Mia Lego, Kyla Ysabelle Dela Cruz, Kent Hervey Gener, Darlene Lapso, Lore Faith Sabio"
date: "2023-12-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Worksheet-5a in R

## 1. Each group needs to extract the top 50 tv shows in Imdb.com. It will include the rank, the title of the tv show, tv rating, the number of people who voted, the number of episodes, the year it was released.

```{r}
library(rvest)
library(httr)
library(dplyr) # use of pipeline %>%
library(polite)

#install.packages("kableExtra")
#kableExtra package is to create tables using the kable() function 

library(kableExtra)



polite::use_manners(save_as = 'polite_scrape.R')

#Specifying the url for desired website to be scraped
url <- 'https://www.imdb.com/chart/toptv/?ref_=nv_tvv_250'

# asking permission to scrape
session <- bow(url,
               user_agent = "Educational")
session

#creating objects for the dataset
rank_title <- character(0)

# scraping in polite way using the h3 element
title_list <- scrape(session) %>%
  html_nodes('h3.ipc-title__text') %>% 
  html_text

# Extracting titles and simple data cleaning process
# we will use the title_list 
class(title_list)

title_list_sub <- as.data.frame(title_list[2:51])

colnames(title_list_sub) <- "ranks"

#split the string(rank and title)
split_df <- strsplit(as.character(title_list_sub$ranks),".",fixed = TRUE)
split_df <- data.frame(do.call(rbind,split_df))

#rename and delete columns
# deleting columns 3 and 4 since it duplicated the columns
split_df <- split_df[-c(3:4)] 

#renaming column 1 and 2
colnames(split_df) <- c("ranks","title") 

rank_title <- data.frame(
  rank_title = split_df)
rank_title<-rank_title[,-3]
colnames(rank_title)<-c("Rank","Title")

#------------------------------------------------------------


rate<- character(0)

# scraping in polite way using the h3 element
rate_list <- scrape(session) %>%
  html_nodes('span.ipc-rating-star--imdb') %>% 
  html_text

# Extracting titles and simple data cleaning process
# we will use the title_list 
class(rate_list)

rate_list_sub <- as.data.frame(rate_list[2:51])

head(rate_list_sub)
tail(rate_list_sub)
#changing column names to ranks
colnames(rate_list_sub) <- "ratings"

#split the string(rank and title)
split_df <- strsplit(as.character(rate_list_sub$ratings), "(",fixed = TRUE)
split_df <- data.frame(do.call(rbind,split_df))

#rename and delete columns
# deleting columns 3 and 4 since it duplicated the columns
split_df <- split_df[-c(3:4)] 

#renaming column 1 and 2
colnames(split_df) <- c("Ratings","Number of Votes") 

# structure of splif_df
str(split_df) 
class(split_df)
head(split_df)
split_dq <- strsplit(as.character(split_df$`Number of Votes`), ")",fixed = TRUE)
split_df<-split_df[,-2]
split_df<-rbind(split_df,split_dq)

split_df<-t(split_df)
split_df

ratings <- data.frame(
  ratings = split_df)
colnames(ratings)<-c("Ratings","Number of Votes")
ratings

next2<-cbind(rank_title,ratings)



#---------------------------------------------------------------------
  

  year<- character(0)

# scraping in polite way using the h3 element
year_list <- scrape(session) %>%
  html_nodes('div.sc-43986a27-7') %>% 
  html_text

# Extracting titles and simple data cleaning process
# we will use the title_list 
class(year_list)

year_list_sub <- as.data.frame(year_list[1:50])


colnames(year_list_sub) <- "ratings"
#split the string(rank and title)
split_df <- gsub("(.{4})", "\\1,", as.character(year_list_sub$ratings), perl=TRUE)
split_df <- data.frame(do.call(rbind, strsplit(split_df, ",")))



#rename and delete columns
# deleting columns 3 and 4 since it duplicated the columns
split_df <- split_df[-c(2:6)] 

#renaming column 1 and 2
colnames(split_df) <- c("Year") 

# structure of splif_df
str(split_df) 
class(split_df)
head(split_df)

next3<-cbind(next2,split_df)
next3
```

## 2. From the 50 tv shows, select at least 5 tv shows to scrape the user reviews that will include the reviewer's name, date of reviewed, user rating, title of the review, and text reviews.

### 1st

```{r}
library(rvest)
library(httr)
library(dplyr) # use of pipeline %>%
library(polite)

#install.packages("kableExtra")
#kableExtra package is to create tables using the kable() function 

library(kableExtra)



polite::use_manners(save_as = 'polite_scrape.R')

#Specifying the url for desired website to be scraped
url <- 'https://www.imdb.com/title/tt0903747/reviews/?ref_=tt_ov_rt'

# asking permission to scrape
session <- bow(url,
               user_agent = "Educational")
session

#creating objects for the dataset
name <- character(0)

# scraping in polite way using the h3 element
title_list <- scrape(session) %>%
  html_nodes('span.display-name-link') %>% 
  html_text



title_list_sub <- as.data.frame(title_list[1:25])


name<- title_list_sub
colnames(name)<-c("Name")

#---------------------------------------------------------------------------

date <- character(0)

# scraping in polite way using the h3 element
date_list <- scrape(session) %>%
  html_nodes('span.review-date') %>% 
  html_text


date_list_sub <- as.data.frame(date_list[1:25])




#rename and delete columns
# deleting columns 3 and 4 since it duplicated the columns


date<- date_list_sub
colnames(date)<-c("Date")


part2<-cbind(name,date)

#---------------------------------------------------------------------------


rating <- character(0)

# scraping in polite way using the h3 element
rate_list <- scrape(session) %>%
  html_nodes('span.rating-other-user-rating') %>% 
  html_text



rate_list_sub <- as.data.frame(rate_list[1:25])

colnames(rate_list_sub) <- "ranks"

#split the string(rank and title)
split_df <- strsplit((rate_list_sub$ranks),"\n",fixed = TRUE)
split_df <- data.frame(do.call(rbind,split_df))



rating<- data.frame(
  rating= split_df)

Rating<-rating[,2]

part3<-cbind(part2,Rating)

#---------------------------------------------------------------------------
title <- character(0)

# scraping in polite way using the h3 element
titles_list <- scrape(session) %>%
  html_nodes('a.title') %>% 
  html_text



titles_list_sub <- as.data.frame(titles_list[1:25])


colnames(titles_list_sub) <- "ranks"

#split the string(rank and title)
split_df <- strsplit((titles_list_sub$ranks),"\n",fixed = TRUE)
split_df <- data.frame(do.call(rbind,split_df))

#rename and delete columns
# deleting columns 3 and 4 since it duplicated the columns


#renaming column 1 and 2



title<- data.frame(
  title= split_df)

colnames(title)<-c("Title of Review")

part4<-cbind(part3,title)


#---------------------------------------------------------------------------


text <- character(0)

# scraping in polite way using the h3 element
text_list <- scrape(session) %>%
  html_nodes('div.text.show-more__control') %>% 
  html_text



text_list_sub <- as.data.frame(text_list[1:25])



colnames(text_list_sub)<-c("Text Reviews")


part5<-cbind(part4,text_list_sub)
part5

write.csv(part5,file="num2_1st_breaking_bad.csv")
```

### 2nd

```{r}
library(rvest)
library(httr)
library(dplyr)
library(polite)

library(kableExtra)



polite::use_manners(save_as = 'polite_scrape.R')


url <- 'https://www.imdb.com/title/tt5491994/reviews/?ref_=tt_ov_rt'

# asking permission to scrape
session <- bow(url,
               user_agent = "Educational")


name <- character(0)

title_list <- scrape(session) %>%
  html_nodes('span.display-name-link') %>% 
  html_text


title_list_sub <- as.data.frame(title_list[1:25])


name<- title_list_sub
colnames(name)<-c("Name")


#---------------------------------------------------------------------------

date <- character(0)


date_list <- scrape(session) %>%
  html_nodes('span.review-date') %>% 
  html_text

date_list_sub <- as.data.frame(date_list[1:25])


date<- date_list_sub
colnames(date)<-c("Date")


part2<-cbind(name,date)

#---------------------------------------------------------------------------


rating <- character(0)

rate_list <- scrape(session) %>%
  html_nodes('span.rating-other-user-rating') %>% 
  html_text


rate_list_sub <- as.data.frame(rate_list[1:25])

colnames(rate_list_sub) <- "ranks"

split_df <- strsplit((rate_list_sub$ranks),"\n",fixed = TRUE)
split_df <- data.frame(do.call(rbind,split_df))

rating<- data.frame(
  rating= split_df)

Rating<-rating[,2]

part3<-cbind(part2,Rating)

#---------------------------------------------------------------------------
title <- character(0)

titles_list <- scrape(session) %>%
  html_nodes('a.title') %>% 
  html_text


titles_list_sub <- as.data.frame(titles_list[1:25])

colnames(titles_list_sub) <- "ranks"

split_df <- strsplit((titles_list_sub$ranks),"\n",fixed = TRUE)
split_df <- data.frame(do.call(rbind,split_df))

title<- data.frame(
  title= split_df)
colnames(title)<-c("Title of Review")
part4<-cbind(part3,title)


#---------------------------------------------------------------------------


text <- character(0)

text_list <- scrape(session) %>%
  html_nodes('div.text.show-more__control') %>% 
  html_text


text_list_sub <- as.data.frame(text_list[1:25])

colnames(text_list_sub)<-c("Text Reviews")


part5<-cbind(part4,text_list_sub)
write.csv(part5,file="num2_2nd_planet_earth_II.csv")
part5



```

### 3rd
```{r}
library(rvest)
library(httr)
library(dplyr) 
library(polite)

library(kableExtra)



polite::use_manners(save_as = 'polite_scrape.R')

url <- 'https://www.imdb.com/title/tt0417299/reviews/?ref_=tt_ov_rt'


session <- bow(url,
               user_agent = "Educational")



name <- character(0)


title_list <- scrape(session) %>%
  html_nodes('span.display-name-link') %>% 
  html_text


title_list_sub <- as.data.frame(title_list[1:25])


name<- title_list_sub
colnames(name)<-c("Name")


#---------------------------------------------------------------------------

date <- character(0)

date_list <- scrape(session) %>%
  html_nodes('span.review-date') %>% 
  html_text

date_list_sub <- as.data.frame(date_list[1:25])

date<- date_list_sub
colnames(date)<-c("Date")


part2<-cbind(name,date)

#---------------------------------------------------------------------------


rating <- character(0)


rate_list <- scrape(session) %>%
  html_nodes('span.rating-other-user-rating') %>% 
  html_text

rate_list_sub <- as.data.frame(rate_list[1:25])

colnames(rate_list_sub) <- "ranks"


split_df <- strsplit((rate_list_sub$ranks),"\n",fixed = TRUE)
split_df <- data.frame(do.call(rbind,split_df))

rating<- data.frame(
  rating= split_df)

Rating<-rating[,2]


part3<-cbind(part2,Rating)

#---------------------------------------------------------------------------
title <- character(0)


titles_list <- scrape(session) %>%
  html_nodes('a.title') %>% 
  html_text

titles_list_sub <- as.data.frame(titles_list[1:25])

colnames(titles_list_sub) <- "ranks"

split_df <- strsplit((titles_list_sub$ranks),"\n",fixed = TRUE)
split_df <- data.frame(do.call(rbind,split_df))


title<- data.frame(
  title= split_df)

colnames(title)<-c("Title of Review")

part4<-cbind(part3,title)


#---------------------------------------------------------------------------


text <- character(0)


text_list <- scrape(session) %>%
  html_nodes('div.text.show-more__control') %>% 
  html_text

text_list_sub <- as.data.frame(text_list[1:25])

colnames(text_list_sub)<-c("Text Reviews")


part5<-cbind(part4,text_list_sub)
part5
write.csv(part5,file="num2_3rd_avatar_reviews.csv")



```

### 4th
```{r}
library(rvest)
library(httr)
library(dplyr)
library(polite)

library(kableExtra)



polite::use_manners(save_as = 'polite_scrape.R')

url <- 'https://www.imdb.com/title/tt2861424/reviews/?ref_=tt_ql_2'


session <- bow(url,
               user_agent = "Educational")

name <- character(0)


title_list <- scrape(session) %>%
  html_nodes('span.display-name-link') %>% 
  html_text

title_list_sub <- as.data.frame(title_list[1:25])


name<- title_list_sub
colnames(name)<-c("Name")


#---------------------------------------------------------------------------

date <- character(0)


date_list <- scrape(session) %>%
  html_nodes('span.review-date') %>% 
  html_text


date_list_sub <- as.data.frame(date_list[1:25])

date<- date_list_sub
colnames(date)<-c("Date")

part2<-cbind(name,date)

#---------------------------------------------------------------------------


rating <- character(0)

rate_list <- scrape(session) %>%
  html_nodes('span.rating-other-user-rating') %>% 
  html_text

rate_list_sub <- as.data.frame(rate_list[1:25])

colnames(rate_list_sub) <- "ranks"

split_df <- strsplit((rate_list_sub$ranks),"\n",fixed = TRUE)
split_df <- data.frame(do.call(rbind,split_df))

rating<- data.frame(
  rating= split_df)

Rating<-rating[,2]

part3<-cbind(part2,Rating)
#---------------------------------------------------------------------------
title <- character(0)

titles_list <- scrape(session) %>%
  html_nodes('a.title') %>% 
  html_text

titles_list_sub <- as.data.frame(titles_list[1:25])

colnames(titles_list_sub) <- "ranks"

split_df <- strsplit((titles_list_sub$ranks),"\n",fixed = TRUE)
split_df <- data.frame(do.call(rbind,split_df))


title<- data.frame(
  title= split_df)
colnames(title)<-c("Title of Review")
part4<-cbind(part3,title)


#---------------------------------------------------------------------------


text <- character(0)

text_list <- scrape(session) %>%
  html_nodes('div.text.show-more__control') %>% 
  html_text

text_list_sub <- as.data.frame(text_list[1:25])

colnames(text_list_sub)<-c("Text Reviews")


part5<-cbind(part4,text_list_sub)
as.data.frame(part5)

write.csv(part5,file="num2_4th_rick&morty.csv")



```

### 5th
```{r}
library(rvest)
library(httr)
library(dplyr) 
library(polite)

library(kableExtra)



polite::use_manners(save_as = 'polite_scrape.R')


url <- 'https://www.imdb.com/title/tt2560140/reviews/?ref_=tt_ql_2'


session <- bow(url,
               user_agent = "Educational")


name <- character(0)

title_list <- scrape(session) %>%
  html_nodes('span.display-name-link') %>% 
  html_text
title_list_sub <- as.data.frame(title_list[1:25])


name<- title_list_sub
colnames(name)<-c("Name")
name

#---------------------------------------------------------------------------

date <- character(0)


date_list <- scrape(session) %>%
  html_nodes('span.review-date') %>% 
  html_text


date_list_sub <- as.data.frame(date_list[1:25])


date<- date_list_sub
colnames(date)<-c("Date")


part2<-cbind(name,date)

#---------------------------------------------------------------------------


rating <- character(0)


rate_list <- scrape(session) %>%
  html_nodes('span.rating-other-user-rating') %>% 
  html_text

rate_list_sub <- as.data.frame(rate_list[1:25])

colnames(rate_list_sub) <- "ranks"


split_df <- strsplit((rate_list_sub$ranks),"\n",fixed = TRUE)
split_df <- data.frame(do.call(rbind,split_df))

rating<- data.frame(
  rating= split_df)

Rating<-rating[,2]


part3<-cbind(part2,Rating)

#---------------------------------------------------------------------------
title <- character(0)


titles_list <- scrape(session) %>%
  html_nodes('a.title') %>% 
  html_text

titles_list_sub <- as.data.frame(titles_list[1:25])
colnames(titles_list_sub) <- "ranks"


split_df <- strsplit((titles_list_sub$ranks),"\n",fixed = TRUE)
split_df <- data.frame(do.call(rbind,split_df))

title<- data.frame(
  title= split_df)

colnames(title)<-c("Title of Review")

part4<-cbind(part3,title)

save(part4,file="p4.csv")
#---------------------------------------------------------------------------


text <- character(0)

text_list <- scrape(session) %>%
  html_nodes('div.text.show-more__control') %>% 
  html_text

text_list_sub <- as.data.frame(text_list[1:25])

colnames(text_list_sub)<-c("Text Reviews")


part5<-cbind(part4,text_list_sub)
write.csv(part5,file="num3_attackontitan.csv")



```

